\section{Addition in GF(2$^{8}$)}

\subsection{A(x) = x$^{7}$ + x$^{5}$ + x$^{3}$ + x$^{2}$ + 1, B(x) = x$^{4}$ + x$^{3}$ + 1}
\label{section:1a}

\subsection{A(x) = x$^{5}$ + $^{x3}$ + x$^{2}$, B(x) = x$^{6}$ + x$^{4}$ + x$^{3}$ + 1}
\label{section:1b}

\subsection{A(x) = x$^{6}$ + x$^{5}$ + x$^{3}$ + x + 1, B(x) = x$^{7}$ + x$^{6}$ + x$^{4}$ + x$^{2}$ + 1}
\label{section:1c}

\subsection{Which effect has the reduction polynome in general on the result of an addition?}
\label{section:1d}


\section{Multiplication in GF(5$^{4}$)}
Consider the finite field F(5$^{4}$) with the irreducible reduction polynome P(x) = x$^{4}$ + x$^{2}$ + 2x + 2.

\subsection{Compute the addition table for this field}
\label{section:2a}
% this means a n  n-table, with the results of the addition of the x- and the y-coordinate (0 to n-1).

\subsection{Compute the multiplication table for this field.}
\label{section:2b}

\subsection{Compute x$^{4}$ mod P(x), x$^{5}$ mod P(x) and x$^{6}$ mod P(x).}
\label{section:2c}

\subsection{Calculate A(x) $\times$ B(x) mod P(x) for A(x) = x$^{4}$ + x$^{1}$ + 2, B(x) = 2x$^{3}$ + 2x$^{2}$ + 1}
\label{section:2d}

\section{Multiplication in GF(2$^{8}$)}

\subsection{Compute A(x) $\times$ B(x) mod P(x) for the following values and give the result in HEX}
\label{section:3a}

\subsection{With which operation is it possible to realise both these multiplications B$_{1}$(x) = x, B$_{2}$(x) = x+1 efficiently}
\label{section:3b}

\section{Avalanche effect in AES}

\subsection{Calculate the respective Output to the Input W after the first round of AES! use the round-keys K$_{0}$, \ldots, K$_{1}$!}
\label{section:4a}

\subsection{Compute all the output bytes for the case that all the input bytes are zero (solution only in HEX)}
\label{section:4b}

\subsection{How many outputbytes have changed now? (We consider just one round of AES)}
\label{section:4c}

\section{Keygeneration in AES}

\subsection{Given is a main key K, consisting of zeros. Find the sub-key K$_{1}$ after the first round of key-generation.}
\label{section:5a}

\subsection{Given is the main key K = (0x00000008; 0x00000004; 0x00000002; 0x00000001). Find the sub-key K$_{1}$ after the first round of key-generation.}
\label{section:5b}


\section{Solution template for Avalanche effect in AES}

\subsection{After conversion of the Input in matrix-form}
\label{section:6a}

\subsection{After conversion of the Input in matrix-form}
\label{section:6b}
